---
title: "Using `relic` with `targets`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{targets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(relic)
```

`relic` is _most_ useful with `targets` when you are version-controlling your
targets objects and data.  This means committing your target objects and files
directly to your git repository, using git LFS to store target objects, and/or
using [versioned cloud storage](https://books.ropensci.org/targets/cloud-storage.html)
to store target objects. For all of these cases, you generally want to commit
your `_targets/meta/meta` file to your git repository. This file contains
information th state of the pipeline.

Even if you are not version-controlling your targets objects and data, you can
still make use of `relic` to inspect your pipeline history and also re-build
targets from previous versions. This vignette shows you how.

# Targets and cloud storage

## Setup

If you want to follow along with this part of the tutorial, you'll need to install the MinIO server and client programs.  These are used to set up a local server that emulates cloud storage.


